### 2021-12-15 documentos/pce.tex
dandole

\subsection{Single qubit case} % {{{

@@

\subsection{Pauli component erasing maps} % {{{

Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$ qubits can be written using Pauli strings in the following way, 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$ such that $r_{\vec \alpha}:=\langle \sigma_{\vec \alpha} \rangle=\tr \left(\rho \sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
of the density matrix in the basis $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$. The components of $\valpha$ range from $0$ to $3$. 
Notice that given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that $r_{\vec 0}=1$. 
{\red We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits. } \ddnote{esto se quita, ya lo definí arriba como Pauli strings.}

As mentioned above, \pce{} maps nullify Pauli strings, thus Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\label{eq:definition:Pauli}
\end{equation}
For the operation to preserve the trace of the density matrix, we require that
$\tau_{\vec 0}=1$.  
% These operations are diagonal in the basis $\left\{
% 2^{-N/2}\sigma_{\vec \alpha} \right\}$, which follows from
% \eref{eq:sigma_property}. 
% The diagonal components are $\taus$, i.e. $\hat
% \mcE=\diag(\taus)$. Additionally, they belong to the subset of unital channels
% that can be written as convex combinations of unitary channels. \cpnote{Alguien 
% puso aca que lo probarian, pero no lo hemos discutido y quizá no le veo 
% el caso en este articulo}

A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations\janote{aquí hay una contradicción
con lo que se dice en la \lr{A1}}. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

@@

\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases de la importancia de esta familia.} \ddnote{De momento no he encontrado
alguna reference, para qubits si, pero para los generales no} \ddnote{Como comento arriba, no le veo sentido que eso esté aqui}.
% Notice
% than in both cases we drop the label $\alpha$ for simplicity, as it will 
% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
% aquí}.

>>>>

\subsection{One qubit \pce{} maps} % {{{

@@

\subsection{$\mathbf{N}$ qubits Pauli component erasing maps} % {{{

Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$ qubits can be written using Pauli strings in the following way, 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$ such that $r_{\vec \alpha}:=\langle \sigma_{\vec \alpha} \rangle=\tr \left(\rho \sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
of the density matrix in the basis $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$. The components of $\valpha$ range from $0$ to $3$. 
Notice that given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that $r_{\vec 0}=1$. Additionally, observe that $\vec r_{\vec \alpha}$ can be understood as a generalization of the Bloch vector for $N$ qubits.

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\label{eq:definition:Pauli}
\end{equation}
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. In the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.

A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
 determine which $\taus$ lead to a valid quantum map.

@@

\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases de la importancia de esta familia.} \ddnote{hecho}.
% Notice
% than in both cases we drop the label $\alpha$ for simplicity, as it will 
% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
% aquí}.
